### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis

\begin{longtable}[]{@{}llll@{}}
\caption{Sensor capabilities merging
\label{Sensor_capabilities_merging.csv}}\tabularnewline
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endfirsthead
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endhead
static & & static & A\tabularnewline
& dynamic & dynamic & B\tabularnewline
axis\_temp & axis\_temp & axis\_temp & A B\tabularnewline
axis\_x & axis\_x & axis\_x & A B\tabularnewline
\bottomrule
\end{longtable}

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command is
received over network.

>>>>

\begin{longtable}[]{@{}llll@{}}
\caption{Sensor capabilities merging algorithm
\label{Sensor_capabilities_merging_algorithm.csv}}\tabularnewline
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endfirsthead
\toprule
SENSOR A & SENSOR B & MERGED CAPABILITIES & CAPABLE SENSORS ID
LUT\tabularnewline
\midrule
\endhead
static & & static & A\tabularnewline
& dynamic & dynamic & B\tabularnewline
axis\_temp & axis\_temp & axis\_temp & A B\tabularnewline
axis\_x & axis\_x & axis\_x & A B\tabularnewline
\bottomrule
\end{longtable}

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
the host when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command
is received over network.
